\documentclass[12pt]{article}
 
\usepackage[margin=1in]{geometry} 
\usepackage{enumitem}

\newenvironment{blockquote}{%
  \par%
  \medskip
  \leftskip=2em%
  \noindent\ignorespaces}{%
  \par\medskip}

\begin{document}
 
\title{Homework 1}
\author{Jacob Nisnevich \textemdash \hspace{2px} 804375355 \\ 
Jason Yang \textemdash \hspace{2px} 804331785 \\
Engr 111}
 
\maketitle
 
\begin{enumerate}
	\renewcommand\labelenumi{\bfseries\theenumi.}
	\item \textbf{(3 points)} Find two companies (of your choice) whose financial statements are
	publicly available. Fill out the following table:

	\begin{table}[ht]
		\centering
		\begin{tabular}{| l | l | l | l | l | l |}
			\hline
			Company & Cash Holdings & Long Term Debt & Equity & Revenue & Net Income \rule{0pt}{2.3ex} \\
			\hline
			\textbf{Google} & \$69,780,000.00 & \$1,944,000.00 & \$111,783,000.00 & \$17,727,000.00 & \$3,931,000.00 \rule{0pt}{2.3ex} \\
			\hline
			\textbf{Facebook} & \$14,125,000.00 & \$110,000.00 & \$39,452,000.00 & \$4,042,000.00 & \$719,000.00 \rule{0pt}{2.3ex} \\
			\hline
		\end{tabular}
	\end{table}

	Can you compare the financial health of these companies by looking at the above numbers? Why or why not?

	\begin{blockquote}
		It is difficult to compare the financial health of the companies with only these numbers because the share price is not listed, which is the best indicator of the past, present, and future financial health of a company. Also these numbers do not represent the current value of assets of these companies. Overall, there are too many additional variables that must be analyzed in order to achieve an accurate comparison.
	\end{blockquote}

	\item \textbf{(3 points)} After reading the copied article (http://www.economist.com/node/21542803), answer the following questions:
	\begin{enumerate}
		\item Why would a company provide ``golden parachute'' to its executives? 
		\begin{blockquote}
			A company would provide a ``golden parachute'' to an executive in order to attempt to persuade the executive or manager to not block a planned takeover or merger.
		\end{blockquote}

		\item Why is the size of the golden parachute important in terms of incentives it creates for the managers?
		\begin{blockquote}
			The size of the ``golden parachute'' is important as larger sums are more likely to incentivize the manager to let the merger or takeover go through.
		\end{blockquote}
	\end{enumerate}

	\item Financial Manager makes various types of decisions related to different aspects of a company’s operations. Determine whether each of the following decisions is a Capital Budgeting, Capital Structure or a Net Working Capital management decision. Note that each case may affect more than one decision.
	\begin{enumerate}
		\item \textbf{(1 point)} Hiring a fresh-out-of-college engineer as the CEO. 
		\begin{blockquote}
			Capital Budgeting, because employees are long-term assets, and hiring a new CEO is a long-term investment. Net Working Capital, because the company setting aside the salary for the CEO is money not being spent managing and financing short-term assets.
		\end{blockquote}
		\item \textbf{(1 point)} Investing the extra cash on a piece of land that is estimated to go up in value versus keeping it in the cash account.
		\begin{blockquote}
			Capital Budgeting, because aquiring land that will go up in value over time is a long-term investment. Net Working Capital, because the company is spending money on a long-term investment rather than financing short-term assets.
		\end{blockquote}
		\item \textbf{(1 point)} Deciding whether to borrow from a financial institution versus issuing and selling new stock shares.
		\begin{blockquote}
			Capital Structure, because raising money from either stocks or bonds from a financial institution are ways for the firm to raise funds for other investments. Net Working Capital, because these additional finances allow the company to finance and manage short-term assets.
		\end{blockquote}
		\item \textbf{(1 point)} Deciding whether to acquire a smaller competitor. 
		\begin{blockquote}
			Capital Budgeting, because acquire a smaller competitor is certainly a long-term investment. Capital Structure, because the firm must then think about how to raise the funds for acquiring the competitor. Net Working Capital, because the use of these finances to acquire the competitor could be used to finance short-term assets.
		\end{blockquote}
	\end{enumerate}
\end{enumerate}

 
\end{document}